Paper

### 2019-12-24 Paper_resubmit.Rmd
...

tt = t.test(subset(complexity.score, Status == 'Progressor')$cx, subset(complexity.score, Status == 'Non-Progressor')$cx)
pv = ggplot(complexity.score, aes(Status, cx, fill=Status)) + 
  geom_jitter(width=0.2, color='grey39') + 
  geom_boxplot(outlier.colour = NA, alpha=0.8) +
  labs(x='', y='cx', title='Per sample cx scores', subtitle=paste('p-value=', format.pval(tt$p.value, digits=2))) + theme(legend.position = 'none') +
  plot.theme
pv
ggsave('plots/per_sample_cx.png', plot=pv + theme(text=element_text(size=12)), width=4, height=4, units='in', dpi=300)

@@

ggsave(filename='plots/auc/training_auc.png', plot=roc.plot(roc), width=6.5, height=4.5, units='in', dpi=300)

@@

rocFirstEndo = pROC::roc(Status ~ avg, data=firstEndo, ci=T, of='thresholds')

rocFirstEndo$model = 'First endoscopy'
ggsave('plots/auc/firstendo_auc.png', plot=roc.plot(rocFirstEndo, title='First Endoscopy'), width=6, height=6, units="in", limitsize=F, dpi = 300)

endo.thresholds = bind_cols('roc'=c('Max','Avg','Last','First'),
  bind_rows(
    pROC::coords(rocEndoM, 'best', transpose=T),
    pROC::coords(rocEndoA, 'best', transpose=T),
    pROC::coords(rocLastEndo, 'best', transpose=T),
    pROC::coords(rocFirstEndo, 'best', transpose=T)
  ))

@@

m = rbind.data.frame(
      get.roc.stat(roc),
      get.roc.stat(rocEndoM),get.roc.stat(rocEndoA),
      get.roc.stat(rocPtM), get.roc.stat(rocPtA),
      get.roc.stat(rocFirstEndo), get.roc.stat(rocLastEndo))
m$model = factor(m$model)

@@

ggsave('plots/auc/multi_auc.png', plot=p, height=6, width=5, units='in',dpi=300)
```

@@

ct = cor.test(pi$p11Loss, (as.numeric(pi$p53.Status)-1))
```

17p11 loss and p53 IHC correlation  R=`r round(ct$estimate,2)`.

@@

max.rules = purrr::map(unique(pg.samp$Patient), function(pt) {
    preds = pg.samp %>% filter(Patient == pt) %>% arrange(Endoscopy.Year, months.before.final)
    endo = BarrettsProgressionRisk:::.setUpRxTablePerEndo(preds %>% dplyr::mutate(Endoscopy = months.before.final, Sample = 'Samplename'), 'max', verbose=F) %>% mutate(Endoscopy = Endoscopy*-1)
    rx = BarrettsProgressionRisk:::.apply.rules(endo, 'Endoscopy', pred.confidence )

@@

>>>>

tt = wilcox.test(subset(complexity.score, Status == 'Progressor')$cx, subset(complexity.score, Status == 'Non-Progressor')$cx)
pv = ggplot(complexity.score, aes(Status, cx, fill=Status)) + 
  geom_jitter(width=0.2, color='grey39') + 
  geom_boxplot(outlier.colour = NA, alpha=0.8) +
  labs(x='', y='cx', title='Per sample cx scores', subtitle=paste('p-value=', format.pval(tt$p.value, digits=2))) + theme(legend.position = 'none') +
  plot.theme
pv
ggsave('plots/per_sample_cx.png', plot=pv + theme(text=element_text(size=12)), width=4, height=4, units='in', dpi=300)

@@

ggsave(filename='plots/auc/training_auc.png', plot=roc.plot(roc), width=6.5, height=4.5, units='in', dpi=300)
ggsave(filename='plots/auc/training_auc_supp.png', plot=roc.plot(roc) + ggtitle('Per sample'), width=6, height=6, units='in', dpi=300)

@@

rocFirstEndo = pROC::roc(Status ~ avg, data=firstEndo, ci=T, of='thresholds')
rocFirstEndo$model = 'First endoscopy'
ggsave('plots/auc/firstendo_auc.png', plot=roc.plot(rocFirstEndo, title='First Endoscopy'), width=6, height=6, units="in", limitsize=F, dpi = 300)

pendo.rand = pg.samp %>% dplyr::group_by(Patient, Status, PID) %>%
  dplyr::summarise( r.Prob = sample(Prediction, 1), n = length(PID) ) %>% filter(n > 1)
rocRandEndo = pROC::roc(Status ~ r.Prob, data=pendo.rand, ci=T, of='thresholds', transpose = T)
rocRandEndo$model = 'Per Endoscopy Random'
ggsave('plots/auc/randomendo_auc.png', plot=roc.plot(rocRandEndo, title='Random per Endoscopy'), width=6, height=6, units="in", limitsize=F, dpi = 300)

endo.thresholds = bind_cols('roc'=c('Max','Avg','Last','First','Random'),
  bind_rows(
    pROC::coords(rocEndoM, 'best', transpose=T),
    pROC::coords(rocEndoA, 'best', transpose=T),
    pROC::coords(rocLastEndo, 'best', transpose=T),
    pROC::coords(rocFirstEndo, 'best', transpose=T),
    pROC::coords(rocRandEndo, 'best', transpose=T)
  ))
```

@@

m = rbind.data.frame(
      get.roc.stat(roc),
      get.roc.stat(rocEndoM),get.roc.stat(rocEndoA),
      get.roc.stat(rocPtM), get.roc.stat(rocPtA),
      get.roc.stat(rocFirstEndo), get.roc.stat(rocLastEndo),
      get.roc.stat(rocRandEndo))

m$model = factor(m$model)

@@

ggsave('plots/auc/multi_auc.png', plot=p, height=6, width=8, units='in',dpi=300)
```

@@

ct = fisher.test(table(pi$p11Loss, pi$p53.Status))

17p11 loss and p53 IHC correlation  Fisher's odds `r ct$estimate`, p-value = `r ct$p.value`.

@@

max.rules = purrr::map(unique(pg.samp$Patient), function(pt) {
    preds = pg.samp %>% filter(Patient == pt) %>% arrange(Endoscopy.Year, months.before.final)
    endo = BarrettsProgressionRisk:::.setUpRxTablePerEndo(preds %>% dplyr::mutate(Endoscopy = months.before.final, Sample = 'Samplename'), 'max', verbose=F) %>% mutate(Endoscopy = Endoscopy*-1)
    rx = BarrettsProgressionRisk:::.apply.rules(endo, 'Endoscopy', pred.confidence,'numeric' )

@@

# Coefficients by # patients

```{r}
cache.dir = '~/Data/BarrettsProgressionRisk/Analysis/models_5e6_all/supp_train_n/insilico_splits/'

purrr::map(list.files(cache.dir, 'loo.Rdata',recursive = T, full.names = T), function(f) {
  load(f,verbose=T)

  length(unique(pg.samp$Patient))

}
